---
output:
  html_document:
    code_folding: hide
    css: styles.css
---

<font size ="5"><center> **Food Vitamin and Mineral Composition**</center></font>

----


The radar charts show the average content of 9 minerals and vitamins in 6 food groups. The dataset comes from [The Official Portal for European Data](https://data.europa.eu/data/datasets/food-composition-database?locale=en).

Since the values of minerals and vitamins are calculated in different units (mg and mcg), I've standardized them  to unit variance for visualizing on the same scale.  

```{r message = FALSE, warning = FALSE, out.width = '100%', fig.align='center'}
library(dplyr)
library(tidyr)
library(stringr)
library(ggradar)
library(scales)
library(cowplot)
library(ggplot2)

text_color = "#353d42"
font = "Avenir Next"

food <- read.csv("/Users/huvi/Downloads/germany_food_composition_vitamins_and_minerals.csv", header = TRUE, sep = ";") %>% 
  select(food = efsaprodcode2_recoded, group = level1, nutrient = NUTRIENT_TEXT, amount = LEVEL) %>% 
  filter(!(group %in% c("Additives,flavours, baking and processing aids", "Products for non-standard diets, food imitates and food supplements or fortifying agents", "Food products for young population", "Human milk", "Starchy roots or tubers and products thereof, sugar plants", "Composite dishes", "Sugar, confectionery and water-based sweet desserts", "Seasoning, sauces and condiments", "Fruit and vegetable juices and nectars", "Legumes, nuts, oilseeds and spices", "Grains and grain-based products", "Animal and vegetable fats and oils", "Alcoholic beverages", "Water and water-based beverages", "Coffee, cocoa, tea and infusions")),
         nutrient %in% c("Calcium (Ca)", "Total iron", "Magnesium (Mg)", "Zinc (Zn)", "Copper (Cu)", "Phosphorus (P)", "Potassium (K)", "vitamin B-12", "vitamin E; alpha-tocopherol equiv from E vitamer activities")) %>% 
  mutate(
    group = case_when(
      group == "Vegetables and vegetable products" ~ "Veggies",
      group == "Fruit and fruit products" ~ "Fruits",
      group == "Meat and meat products" ~ "Meat",
      group == "Fish, seafood, amphibians, reptiles and invertebrates" ~ "Seafood",
      group == "Milk and dairy products" ~ "Dairy",
      group == "Eggs and egg products" ~ "Egg"
    ),
    nutrient = case_when(
      nutrient == "Calcium (Ca)" ~ "Calcium",
      nutrient == "Total iron" ~ "Iron",
      nutrient == "Magnesium (Mg)" ~ "Magnesium",
      nutrient == "Zinc (Zn)" ~ "Zinc",
      nutrient == "Copper (Cu)" ~ "Copper",
      nutrient == "Phosphorus (P)" ~ "Phosphorus",
      nutrient == "Potassium (K)" ~ "Potassium",
      nutrient == "vitamin B-12" ~ "Vitamin B12",
      nutrient == "vitamin E; alpha-tocopherol equiv from E vitamer activities" ~ "Vitamin E"
    )
  )
  
food$amount = str_replace(food$amount, ",", ".")

         
food_subset <- food %>% 
  filter(food %in% c("Hen eggs", "Duck eggs", "Geese eggs", "Quail eggs",
  "Cow milk, whole", "Cottage cheese", "Yoghurt, cow milk, plain", "Cream, plain",
  "Freshwater fish", "Octopuses", "Lobster, european", "Shrimps and prawns",
  "Bovine fresh meat", "Pig fresh meat", "Chicken fresh meat", "Goat fresh meat",
  "Broccoli and similar-", "Kales and similar-", "Tomatoes and similar-", "Cucumbers",
  "Strawberries and similar-","Apples and similar-", "Common banana", "Avocados")) %>% 
  mutate(
    food = case_when(
      food == "Cow milk, whole" ~ "Cow milk",
      food == "Yoghurt, cow milk, plain" ~ "Yoghurt",
      food == "Cream, plain" ~ "Plain cream",
      food == "Lobster, european" ~ "Lobster",
      food == "Bovine fresh meat" ~ "Beef",
      food == "Pig fresh meat" ~ "Pork",
      food == "Chicken fresh meat" ~ "Chicken",
      food == "Goat fresh meat" ~ "Goat meat",
      food == "Broccoli and similar-" ~ "Broccoli",
      food == "Kales and similar-" ~ "Kales",
      food == "Tomatoes and similar-" ~ "Tomatoes",
      food == "Strawberries and similar-" ~ "Strawberries",
      food == "Apples and similar-" ~ "Apples",
      food == "Common banana" ~ "Bananas",
      TRUE ~ as.character(food)
    ),
    amount = as.numeric(amount)
  ) 

test <- pivot_wider(food_subset, names_from = nutrient, values_from = amount) %>%
  mutate_each(funs(rescale),-c(group, food)) %>% 
  select(food, Calcium:Copper, group)
```

<font size ="5"><center> **Vegetables**</center></font>
```{r message = FALSE, warning = FALSE, out.width = '100%', fig.align='center'}
broccoli <- ggradar(test[1,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#15983DFF",
        plot.title = "Broccoli") +
    theme(plot.title = element_text(family = font, color = "#15983DFF", size = 13, hjust = 0.5, face = "bold"))

kales <- ggradar(test[2,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#15983DFF",
        plot.title = "Kales") +
    theme(plot.title = element_text(family = font, color = "#15983DFF", size = 13, hjust = 0.5, face = "bold"))

tomatoes <- ggradar(test[3,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#15983DFF",
        plot.title = "Tomatoes") +
    theme(plot.title = element_text(family = font, color = "#15983DFF", size = 13, hjust = 0.5, face = "bold"))

cucumbers <- ggradar(test[4,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#15983DFF",
        plot.title = "Cucumbers") +
    theme(plot.title = element_text(family = font, color = "#15983DFF", size = 13, hjust = 0.5, face = "bold"))

plot_grid(broccoli, kales, tomatoes, cucumbers, nrow = 2)
```

<font size ="5"><center> **Fruits**</center></font>
```{r message = FALSE, warning = FALSE, out.width = '100%', fig.align='center'}
apples <- ggradar(test[5,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EC579AFF",
        plot.title = "Apples") +
    theme(plot.title = element_text(family = font, color = "#EC579AFF", size = 13, hjust = 0.5, face = "bold"))

strawberries <- ggradar(test[6,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EC579AFF",
        plot.title = "Strawberries") +
    theme(plot.title = element_text(family = font, color = "#EC579AFF", size = 13, hjust = 0.5, face = "bold"))

avocadoes <- ggradar(test[7,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EC579AFF",
        plot.title = "Avocadoes") +
    theme(plot.title = element_text(family = font, color = "#EC579AFF", size = 13, hjust = 0.5, face = "bold"))

bananas <- ggradar(test[8,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EC579AFF",
        plot.title = "Bananas") +
    theme(plot.title = element_text(family = font, color = "#EC579AFF", size = 13, hjust = 0.5, face = "bold"))

plot_grid(apples, strawberries, avocadoes, bananas, nrow = 2)
```

<font size ="5"><center> **Meat**</center></font>
```{r message = FALSE, warning = FALSE, out.width = '100%', fig.align='center'}
beef <- ggradar(test[9,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EE0011FF",
        plot.title = "Beef") +
    theme(plot.title = element_text(family = font, color = "#EE0011FF", size = 13, hjust = 0.5, face = "bold"))

pork <- ggradar(test[10,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EE0011FF",
        plot.title = "Pork") +
    theme(plot.title = element_text(family = font, color = "#EE0011FF", size = 13, hjust = 0.5, face = "bold"))

goat <- ggradar(test[7,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EE0011FF",
        plot.title = "Goat meat") +
    theme(plot.title = element_text(family = font, color = "#EE0011FF", size = 13, hjust = 0.5, face = "bold"))

chicken <- ggradar(test[8,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#EE0011FF",
        plot.title = "Chicken") +
    theme(plot.title = element_text(family = font, color = "#EE0011FF", size = 13, hjust = 0.5, face = "bold"))

plot_grid(beef, pork, goat, chicken, nrow = 2)
```

<font size ="5"><center> **Seafood**</center></font>
```{r message = FALSE, warning = FALSE, out.width = '100%', fig.align='center'}
fish <- ggradar(test[13,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#149BEDFF",
        plot.title = "Fish") +
    theme(plot.title = element_text(family = font, color = "#149BEDFF", size = 13, hjust = 0.5, face = "bold"))

lobster <- ggradar(test[14,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#149BEDFF",
        plot.title = "Lobsters") +
    theme(plot.title = element_text(family = font, color = "#149BEDFF", size = 13, hjust = 0.5, face = "bold"))

shrimp <- ggradar(test[15,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#149BEDFF",
        plot.title = "Shrimps") +
    theme(plot.title = element_text(family = font, color = "#149BEDFF", size = 13, hjust = 0.5, face = "bold"))

octopus <- ggradar(test[16,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#149BEDFF",
        plot.title = "Octopuses") +
    theme(plot.title = element_text(family = font, color = "#149BEDFF", size = 13, hjust = 0.5, face = "bold"))

plot_grid(fish, lobster, shrimp, octopus, nrow = 2)
```

<font size ="5"><center> **Dairy Products**</center></font>
```{r message = FALSE, warning = FALSE, out.width = '100%', fig.align='center'}
milk <- ggradar(test[17,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#9A703EFF",
        plot.title = "Cow milk") +
    theme(plot.title = element_text(family = font, color = "#9A703EFF", size = 13, hjust = 0.5, face = "bold"))

cream <- ggradar(test[18,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#9A703EFF",
        plot.title = "Plain cream") +
    theme(plot.title = element_text(family = font, color = "#9A703EFF", size = 13, hjust = 0.5, face = "bold"))

yoghurt <- ggradar(test[19,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#9A703EFF",
        plot.title = "Yoghurt") +
    theme(plot.title = element_text(family = font, color = "#9A703EFF", size = 13, hjust = 0.5, face = "bold"))

cheese <- ggradar(test[20,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#9A703EFF",
        plot.title = "Cottage cheese") +
    theme(plot.title = element_text(family = font, color = "#9A703EFF", size = 13, hjust = 0.5, face = "bold"))

plot_grid(milk, cream, yoghurt, cheese, nrow = 2)
```

<font size ="5"><center> **Eggs**</center></font>
```{r message = FALSE, warning = FALSE, out.width = '100%', fig.align='center'}
hen <- ggradar(test[21,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#FEC10BFF",
        plot.title = "Hen eggs") +
    theme(plot.title = element_text(family = font, color = "#FEC10BFF", size = 13, hjust = 0.5, face = "bold"))

duck <- ggradar(test[22,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#FEC10BFF",
        plot.title = "Duck eggs") +
    theme(plot.title = element_text(family = font, color = "#FEC10BFF", size = 13, hjust = 0.5, face = "bold"))

geese <- ggradar(test[23,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#FEC10BFF",
        plot.title = "Geese eggs") +
    theme(plot.title = element_text(family = font, color = "#FEC10BFF", size = 13, hjust = 0.5, face = "bold"))

quail <- ggradar(test[24,1:10],
        base.size = 15, font.radar = font,
        plot.extent.x.sf = 1, plot.extent.y.sf = 1.15,
        grid.line.width = 0.1,
        gridline.min.linetype = "solid", gridline.mid.linetype = "solid", gridline.max.linetype = "solid",
        gridline.min.colour = "#cbcbcb",  gridline.mid.colour = "#cbcbcb",  gridline.max.colour = "#cbcbcb",
        grid.label.size = 2, gridline.label.offset = -0.15,
        axis.label.size = 2, axis.label.offset = 1.14,
        axis.line.colour = "#cbcbcb",
        group.line.width = 0.5, group.point.size = 0.5,
        group.colours = "#FEC10BFF",
        plot.title = "Quail eggs") +
    theme(plot.title = element_text(family = font, color = "#FEC10BFF", size = 13, hjust = 0.5, face = "bold"))

plot_grid(hen, duck, geese, quail, nrow = 2)
```

